Comparing summed probability distributions of shoreline and radiocarbon dates from the Mesolithic Skagerrak coast of Norway

### 2023-09-25 analysis/paper/paper.Rmd
Updated description, added DOI to Zenodo repository
Minor edits to paper. Updated gitignore

All analyses done in this study were performed using the R programming language [@rcoreteam]. Underlying data and programming code used for the paper is available in an online repository at https://doi.org/10.17605/osf.io/fqwt5. This is structured as a research compendium following @marwick2018b, to allow for reproducibility of the results [see also @Marwick2017]. Analysis of the ^14^C-dates was done using the R packages *ADMUR* v1.0.3 [@timpson2021] and *rcarbon* v1.4.4 [@crema2021]. The R package *shoredate* v1.0.2 was used for performing and handling the shoreline dating of sites [@roalkvam2023b], with re-purposed code from both *ADMUR* and *rcarbon* for subsequent Monte Carlo simulation and model comparison.

@@

>>>>

All analyses done in this study were performed using the R programming language [@rcoreteam]. Underlying data and programming code used for the paper is available in an online repository at https://doi.org/10.5281/zenodo.8373857. This is structured as a research compendium following @marwick2018b, to allow for reproducibility of the results [see also @Marwick2017]. Analysis of the ^14^C-dates was done using the R packages *ADMUR* v1.0.3 [@timpson2021] and *rcarbon* v1.4.4 [@crema2021]. The R package *shoredate* v1.0.2 was used for performing and handling the shoreline dating of sites [@roalkvam2023b], with re-purposed code from both *ADMUR* and *rcarbon* for subsequent Monte Carlo simulation and model comparison.

@@

# Declaration of competing interest{-}
The authors have no competing interests to declare.
